---
title: "LBB_Data Visualization_Insurance Dataset"
author: "yohanesegipratama"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Deskripsi Variabel

age: age of primary beneficiary

sex: insurance contractor gender, female, male

bmi: Body mass index, providing an understanding of body, weights that are relatively high or low         relative to height, objective index of body weight (kg / m ^ 2) using the ratio of height to         weight, ideally 18.5 to 24.9

children  : Number of children covered by health insurance / Number of dependents

smoker    : Smoking

region    : the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

charges   : Individual medical costs billed by health insurance

#import library

library(tidyverse)
library(ggplot2)

#load data
```{r}
df = read.csv('data_input/insurance.csv', header = TRUE)
```


```{r}
head(df)
```

```{r}
summary(df)
```
#Data Preprocessing

```{r}
str(df)
```

##check missing vallue
```{r}
colSums(is.na(df))
```

##check duplikat data
```{r}
##check duplikat data
sum(duplicated(df))
```
```{r}
cat("\ndata duplikat")
df[duplicated(df),]
```
```{r}
df <- df %>% distinct()
```

#exploratory data analysis

```{r}

ggplot(df,aes(x = charges, color = smoker))+
  geom_histogram(fill = "white", position = "dodge")+
  theme(legend.position = "top")
```

* insight
berdasarkan visualisasi diatas dapat diketahui, ternyata banyak tidak perokok (perokok pasif)

```{r}
options(repr.plot.width=7, repr.plot.height=5)
ggplot(df, aes(x=log(charges))) +
    geom_histogram(aes(y=..density..),color="black", fill="pink", bins=40) +
    geom_density(color="blue") +
    geom_vline(aes(xintercept= mean(log(charges))), color="blue", linetype="dashed", size=1) +
    geom_vline(aes(xintercept= median(log(charges))), color="red", linetype="dashed", size=1)
```
* insight
berdasarkan grafik histogram diatas data cenderung kekanan (skew-to-right-distribution)



```{r}
ggplot(df)+
  geom_violin(mapping = aes(x = smoker, y = charges, fill = sex), draw_quantiles = (c(0.25,0.5,0.75)))
```
* insight
violin plot diatas dapat disimpulkan bahwa distribusi jenis kelamin lebih banyak perokok